Effects of the body force on the evacuation dynamics

### 2020-01-01 paper.tex
mejore el grafico de degree vs dens y agregue un parrafo en resultados

\begin{figure}[!htbp]
\centering
    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./network_vd2_kn0.eps}\label{network_vd2_kn0}}\ 
    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./network_vd10_kn0.eps}\label{network_vd10_kn0}}\\
        \subfloat[]{\includegraphics[width=0.45\columnwidth]{./network_vd2_kn1200000.eps}\label{network_vd2_kn1200000}}\ 
    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./network_vd10_kn1200000.eps}\label{network_vd10_kn1200000}}\\
\caption[width=0.47\columnwidth]{Contact networks of a 225 pedestrian evacuation through a bottleneck. The door is placed at $(x,y)=(20,10)$~m, the width of the door is 0.92~m (equivalent to 2 pedestrian\textsc{\char13}s diameter). The lines that connect the nodes (pedestrians) represent the contact between them. The color represents the degree (the number of pedestrians with which it is connected). \ref{network_vd2_kn0} and \ref{network_vd10_kn0} correspond to a simulation without body force with $v_d=$2 and $v_d=$10 respectively. \ref{network_vd2_kn1200000} and \ref{network_vd10_kn1200000} correspond to simulations with $k$=1.2~E6 with $v_d=$2 and $v_d=$10 respectively.}
\label{network_bottleneck}
\end{figure}

@@

\begin{figure}[!htbp]
\centering
    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./flow-density_multifric_nobodyforce.eps}\label{flow_density_no_body_force}}\ 
    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./flow-density_multifric_bodyforce.eps}\label{flow_density_body_force}}\\
\caption[width=0.47\columnwidth]{Flow vs. global density. The flow is calculated in a circular area of R=1~m at the center of the corridor. The circular markers correspond to the original friction of the SFM, the "+" symbol corresponds to the friction increased by a factor of five and the triangles correspond to the friction increased by a factor of ten. The desired velocity was $v_d=1$ in all the cases. Fig.~\ref{flow_density_no_body_force} corresponds to simulations without body force and Fig. \ref{flow_density_body_force} corresponds to a body force with $k=$1.2~E5.}
\label{flow_density}
\end{figure}

@@

As was mentioned above, increasing the $k$ value of the body force increases the stiffness of pedestrians. Increasing the stiffness reduces the overlap (both in bottleneck and corridor) and reduces the mean degree in a bottleneck but increases the mean degree in a corridor. In Fig.~\ref{network_corridor} it shown the contact network corresponding to the corridor at a particular timestep and a particular global density. Fig.~\ref{network_d6_kn0} corresponds to $k=0$ while Fig. \ref{network_d6_knE5} corresponds to $k=1.2$~E5. This is an example to show that increasing the stiffness increases the number of contacts between pedestrians (the network connectivity). Notice that there are many more pedestrians with degree 6 in the case of $k=1.2$~E5 than the case of $k=0$. \\

@@

The increment of the clusterization is responsible for the reduction of the flow. In the corridor geometry, the crowd gets more clusterized if the pedestrians become stiffer. We studied the network properties of the contact graph arising from the positions $(x,y)$ of every pedestrian. We found that a good descriptor to exhibit the connectivity is the number of triangles per node. A triangle is defined as a structure composed of three nodes all in contact with each other. Fig.~\ref{triangles} shows the triangles per node as a function of the global density for different stiffness values $k$. This descriptor allows to distinguish states with the same global density but different stiffness levels. In other words, it is a descriptor very sensitive to changes in stiffness that allow expressing the connectivity of the system even better than the mean degree. \\

>>>>

\begin{figure}[!htbp]
\centering
    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./network_vd2_kn0.eps}\label{network_vd2_kn0}}\ 
    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./network_vd10_kn0.eps}\label{network_vd10_kn0}}\\
        \subfloat[]{\includegraphics[width=0.45\columnwidth]{./network_vd2_kn1200000.eps}\label{network_vd2_kn1200000}}\ 
    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./network_vd10_kn1200000.eps}\label{network_vd10_kn1200000}}\\
\caption[width=0.47\columnwidth]{Contact networks of a 225 pedestrian evacuation through a bottleneck. The door is placed at $(x,y)=(20,10)$~m, the width of the door is 0.92~m (equivalent to 2 pedestrian\textsc{\char13}s diameter). The lines that connect the nodes (pedestrians) represent the contact between them. The color represents the degree (the number of pedestrians with which it is connected). (a) and (b) correspond to a simulation without body force with $v_d=$2 and $v_d=$10 respectively. (c) and (d) correspond to simulations with $k$=1.2~E6 with $v_d=$2 and $v_d=$10 respectively.}
\label{network_bottleneck}
\end{figure}

@@

\begin{figure}[!htbp]
\centering
    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./flow-density_multifric_nobodyforce.eps}\label{flow_density_no_body_force}}\ 
    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./flow-density_multifric_bodyforce.eps}\label{flow_density_body_force}}\\
\caption[width=0.47\columnwidth]{Flow vs. global density. The flow is calculated in a circular area of R=1~m at the center of the corridor. The circular markers correspond to the original friction of the SFM, the "+" symbol corresponds to the friction increased by a factor of five and the triangles correspond to the friction increased by a factor of ten. The desired velocity was $v_d=1$ in all the cases. (a) corresponds to simulations without body force and (b) corresponds to a body force with $k=$1.2~E5.}
\label{flow_density}
\end{figure}

@@

As was mentioned above, increasing the $k$ value of the body force increases the stiffness of pedestrians. Increasing the stiffness reduces the overlap (both in bottleneck and corridor). Regarding the network connectivity, increasing the stiffness reduces the mean degree in a bottleneck but increases the mean degree in a corridor. In Fig.~\ref{network_corridor} it shown the contact network corresponding to the corridor at a particular timestep and a particular global density. Fig.~\ref{network_d6_kn0} corresponds to $k=0$ while Fig. \ref{network_d6_knE5} corresponds to $k=1.2$~E5. This is an example to show that increasing the stiffness increases the number of contacts between pedestrians (the network connectivity). Notice that there are many more pedestrians with degree 6 in the case of $k=1.2$~E5 than the case of $k=0$. \\

This result is exactly the opposite of what we get in the bottleneck. This happens because, in the corridor, the lateral walls act like containers that force the pedestrian to increase their contacts. Whereas in the bottleneck there are no lateral walls. Thus, when increasing the stiffness they have more space to detach from each other, reducing the connectedness (hence reducing the mean degree). \\

@@

The increment of the connectedness is responsible for the reduction of the flow. In the corridor geometry, the crowd gets more connected if the pedestrians become stiffer. We studied the network properties of the contact graph arising from the positions $(x,y)$ of every pedestrian. We found that a good descriptor to exhibit the connectivity is the number of triangles per node. A triangle is defined as a structure composed of three nodes all in contact with each other. Fig.~\ref{triangles} shows the triangles per node as a function of the global density for different stiffness values $k$. This descriptor allows to distinguish states with the same global density but different stiffness levels. In other words, it is a descriptor very sensitive to changes in stiffness that allow expressing the connectivity of the system even better than the mean degree. \\
